### 2016-12-21 Plos-one-manuscript/latex/manuscript.tex
working

A small amount of parrifin wax is applyed to the screw to prevent slop from causeing the set point to drift after each acuation.
The nut is sunk in to the hex inset in the body part.
The bolt is threaded in from the top of the body into the nut.
Springs and washers are threaded onto the plunger of the 1 mL syringe for the 30-300 uL configuration.
Springs are placed inside the 3 mL syringe for the 100-1000 mL configuration.
The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly.

@@

\subsection*{Validation}
The printed pipette’s accuracy and precision was characterized and compared to a commercial pipette as well as ISO 8655.
The printed pipette was adjusted to the the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for transfer variability.
Data was taken for printed pipettes with existing graduations as well as with the adjusted scale.
The commerical pipette was adjusted to the desired volume and 5 transfers were taken.

@@

This pipette improves on existing open design pipettes in several ways. 
It requires only two printed parts, a syringe, and some hardware.
It is able to reach into a 15 mL conical tube which is a routine requirement for cell culture.
No permanent connections using tape or glue are required for assembly allowing worn out or broken part to be replaced easily.
Assembly does not require a membrane that may wear or stretch and require tedious replacement.
No validation or calibration is required.
The pipette can be assembled and used to accurately pipette without first validating with a scale.

>>>>

A small amount of parrifin wax is applyed to the screw to prevent slop from causeting the set point to drift after each acuation.
The nut is sunk in to the hex inset in the body part.
The bolt is threaded in from the top of the body into the nut.
Springs and washers are threaded onto the plunger of the 1 mL syringe for the 30-300 uL configuration.
Springs are placed inside the 3 mL syringe for the 100-1000 mL configuration.
The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly.

@@

\subsection*{Validation}
The printed pipette’s accuracy and precision was characterized and compared to a commercial pipette as well as ISO 8655.
The printed pipette was adjusted to the the target volume by eye from the syringe graduations, and the resulting volume was measured and repeated 5 times to account for transfer variability.
Data was taken for printed pipettes with existing graduations as well as with the adjusted scale.
The commerical pipette was adjusted to the desired volume and 5 transfers were taken.
The systematic error and random error was calculated according to ISO 8655 (Table~\ref{table3,table4}).

@@

This pipette improves on existing open design pipettes in several ways. 
Most significatly the user is able to adjust the syringe accuratly without verifying the volume with a scale.
In additon the assembly requires no permanent connections using tape or glue which allows for re-configurationorn and easy replacment of parts.
Our pipette is able to transfer from the bottom of a 15 mL conical tube which is a requirement for many routine lab procedures such as aspirating supernatant from a centrifuged cell pellet.
This design does not use a membrane that may wear out and require tedious replacement.
